### 2013-09-02 doc/taxize_withcode_app.tex
small edit to fix references in appendix

\begin{figure}[H]
\centering
\includegraphics[width=7in,height=8in]{figure/map.pdf}
\caption{A phylogeny}
\end{figure}

@@

Trait-based approaches are a promising tool in ecology. Unlike taxonomy-based methods, traits may not be constrained to biogeographic boundaries [26] and have potential to disentangle the effects of multiple stressors [24].

To analyse trait-composition abundance data must be matched with trait databases like [25]. However these two datatables may contain species information on different taxonomic levels and perhaps data must be aggregated to a joint taxonomic level.

@@

Now we can create \emph{species x sites} and \emph{traits x species} matrices, which could be plugged into methods to analyse trait responses [27].

>>>>

\begin{figure}[H]
\centering
\includegraphics[width=7in,height=8in]{figure/map.pdf}
\caption{A map}
\end{figure}

@@

Trait-based approaches are a promising tool in ecology. Unlike taxonomy-based methods, traits may not be constrained to biogeographic boundaries [27] and have potential to disentangle the effects of multiple stressors [25].

To analyse trait-composition abundance data must be matched with trait databases like [26]. However these two datatables may contain species information on different taxonomic levels and perhaps data must be aggregated to a joint taxonomic level.

@@

Now we can create \emph{species x sites} and \emph{traits x species} matrices, which could be plugged into methods to analyse trait responses [28].

### 2013-09-02 doc/taxize_withcode_appB.Rnw
small edit to fix references in appendix

Trait-based approaches are a promising tool in ecology. Unlike taxonomy-based methods, traits may not be constrained to biogeographic boundaries [26] and have potential to disentangle the effects of multiple stressors [24].

>>>>

Trait-based approaches are a promising tool in ecology. Unlike taxonomy-based methods, traits may not be constrained to biogeographic boundaries [27] and have potential to disentangle the effects of multiple stressors [24].
